Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-05-09 code/rmarkdown/article.Rmd
+ article fixes + remove unneeded comments from MLPE.R
Former-commit-id: ee0043520642de57e7be9a2a46e563d35abc1e75

Second, we used PCAs to identify outlier loci using methods implemented in the \texttt{pcadapt R} package [version 3.0; @r487; @r496]. To enable comparisons between the two outlier detection analyses, we used the same individuals in this analysis as used in the \texttt{BayeScan} analysis. For each of the 26 species, we first imputed missing loci data to permit further analysis. Specifically, the value for a given individual at a given locus was replaced with the mean frequency of that locus among all individuals. Next, we ran a PCA and extracted the minimum number of components needed to secure `r pcadapt.params.LST[[MODE]]$min.variance.explained` % of the variation in loci. We then used Mahalanobis distances [@r398] to compute _P_ values and then q-values [using the \texttt{qvalue R} package; @r491]. Outlier loci were detected using a suitable FDR ($q < `r pcadapt.params.LST[[MODE]]$alpha.level`$).

After classifying loci as adaptive or neutral, we mapped the main gradients of the adaptive (if detected) and neutral genetic variation for each species (Figures S29--S54). For each species, we discarded the population groupings, and partitioned adaptive and neutral loci into separate matrices. We used non-metric multi-dimensional scaling [NMDS; implemented in the \texttt{vegan R} package; @r458] using Gower distances [@r464; using the \texttt{cluster R} package to accommodate sparsity; @r457] to derive continuous variables that described the main gradients of adaptive and neutral genetic variation separately for each species (Table S2). To ensure that the ordinations described a sufficient amount of the genomic variation, we ran successive scaling analyses with increasing dimensionality until this was achieved (maximum stress value $\leq$ `r nmds.params.LST[[MODE]]$max.stress`; `r nmds.params.LST[[MODE]]$trymax` random starts for each analysis). Since each grid cell had up to three samples per species, we used the average of the ordinated values associated with the individuals in each grid cell to express the typical genomic characteristics of individuals in the cells.

@@

## Results
<!-- summary of methods -->
We successfully mapped the main spatial patterns of adaptive (if present) and neutral variation for each of the 26 species. The outlier detection methods detected adaptive genetic variation in `r as.character(as.english(length(env.surrogacy.LST)))` species. Generally, two outlier detection methods gave fairly consistent results (mean `r round(mean(spp.outlier.methods.congruence, na.rm=TRUE),2)` % loci per species $\pm$ `r round(sd(spp.outlier.methods.congruence, na.rm=TRUE),2)` SD). Of the species that were associated with adaptive genetic variation, only a few loci were detected as under selection (mean `r round(mean(spp.outlier.loci.props, na.rm=TRUE),2)` % loci per species $\pm$ `r round(sd(spp.outlier.loci.props, na.rm=TRUE),2)` SD). After identifying the loci under selection, we used NMDS analyses to identify the main gradients of adaptive (if detected) and neutral variation for each species. Generally, only a couple of continuous dimensions were needed to sufficiently describe the adaptive genetic variation for each species (all species $K = 2$; Table S2). On the other hand, a few more continuous dimensions were often needed for neutral genetic variation for each species (minimum $K = `r min(neutral.k)`$; mean $K = `r round(mean(neutral.k),2)`$; max $K = `r max(neutral.k)`$; Table S2). The ordinations resulting from the NMDS analyses were used to construct an adaptive (if present) and neutral genetic space for each species. The spatial distribution of these genetic spaces (Figures S29--S54) generally show patterns of spatial autocorrelation--especially the adaptive genetic spaces (eg.XXXX; SXX). Additionally, most species show east-west patterns in their intra-specific genetic variation (eg. XXXX; SXXX).

<!-- correlation analysis -->
The dissimilarity matrices generated using the surrogate variables correlated with the dissimilarity matrices based on the genetic characteristics of individuals for most species (Table 1). Specifically, environmental variation was found to significantly correlate with adaptive genetic variation for `r as.character(as.english(sum(correlation.model.summary.DF$Environmental.corr.P<0.05,na.rm=TRUE)))` species (`r round((sum(correlation.model.summary.DF$Environmental.corr.P<0.05,na.rm=TRUE)/length(na.omit(correlation.model.summary.DF$Environmental.corr.P)))*100,2)` % associated with loci under selection; _P_ < 0.05; mean `r round(mean(filter(correlation.model.summary.DF, Environmental.corr.P<0.05)$Environmental.Marginal.R2),2)` marginal $R^2$ $\pm$ `r round(sd(filter(correlation.model.summary.DF, Environmental.corr.P<0.05)$Environmental.Marginal.R2),2)` SD for significant models). Additionally, geographic distances between planning units were found to significantly correlate with neutral genetic variation among planning units for `r sum(correlation.model.summary.DF$Geographic.corr.P<0.05,na.rm=TRUE)` species (`r round((sum(correlation.model.summary.DF$Geographic.corr.P<0.05)/length(na.omit(correlation.model.summary.DF$Geographic.corr.P)))*100,2)` % of all the species investigated; _P_ < 0.05; mean `r round(mean(filter(correlation.model.summary.DF, Geographic.corr.P<0.05)$Geographic.Marginal.R2),2)` marginal $R^2$ $\pm$ `r round(sd(filter(correlation.model.summary.DF, Geographic.corr.P<0.05)$Geographic.Marginal.R2),2)` SD for significant models). These results suggest that prioritizations with different environmental characteristics tend to have individuals with different adaptive genetic characteristics. Similarly, planning units that are further apart tend to have individuals with different neutral genetic characteristics. After verifying that the geographic and environmental variables correlate with genetic variation, the next step was to determine how effective these variables were as surrogates in the context of conservation planning.

<!-- surrogacy analysis -->
The environmental and geographic variables were moderately effective surrogates for genetic variation in most species (Figure 2). The relationship between the proportion of adaptive genetic variation secured in a prioritization and the proportion environment variation it also secured differed depending on the species for which the prioritization was generated (${\chi^2}_{`r env.surrogacy.AOV$df[[4]]`} = {`r round(env.surrogacy.AOV$Resid..Dev[[4]],2)`} P = `r pvalString(env.surrogacy.AOV$Pr..Chi.[[4]])`$). The slope for each species were all significantly different to zero (minimum \textit{z} = `r round(max(env.surrogate.spp.DF$statistic),2)`; maximum $P = `r  pvalString(max(env.surrogate.spp.DF$p.value))`$; Table S3). The explanatory power of the environmental surrogates were also generally quite high for most species (mean `r round(mean(env.surrogate.spp.DF$r2CU),2)` $R^2 \pm$ `r round(sd(env.surrogate.spp.DF$r2CU),2)` SD; Figure S56), with exception to _Carex sempervirens_. The nature of these relationships suggest that most of the adaptive variation for a given species can be secured in a prioritization using moderately high environmental-based targets. Similarly, the proportion of neutral genetic variation in a prioritization was affected by the interaction between species and the proportion of neutral variation secured in the prioritization (${\chi^2}_{`r geo.surrogacy.AOV$df[[4]]`} = `r round(geo.surrogacy.AOV$Resid..Dev[[4]],2)`$; $P$ = `r pvalString(geo.surrogacy.AOV$Pr..Chi.[[4]])`). The slope for each species were also significantly different to zero (minimum $z value = `r min(geo.surrogate.spp.DF$statistic)`$; maximum $P = `r max(env.surrogate.spp.DF$p.value)`; Table S3). Generally, the explanatory power of geographic variables were higher than that of environmental variables (mean `r round(mean(geo.surrogate.spp.DF$r2CU),2)` $R^2 \pm$ `r round(sd(geo.surrogate.spp.DF$r2CU),2)` SD; Figure S57). Compared to the environmental variables, the slopes of the relationships suggest that very high geographic-based targets are required to generate prioritizations that secure a sufficient proportion of neutral genetic variation for most species. Additionally, all species were associated with prioritizations that secured a large proportion of environmental or geographic variation (> 70 %), yet preserved only a very small proportion of the genetic variation (< 10 %). These results suggest while prioritizations generated using surrogate-based targets tend to secure more genetic variation, prioritizations generated using just these targets can result in poor solutions.

>>>>

Second, we used PCAs to identify outlier loci using methods implemented in the \texttt{pcadapt R} package [version 3.0; @r487; @r496]. To enable comparisons between the two outlier detection analyses, we used the same individuals in this analysis as used in the \texttt{BayeScan} analysis. For each of the 26 species, we first imputed missing data to permit further analysis. Specifically, the value for a given individual at a given locus was replaced with the mean frequency of that locus among all conspecifics. Next, we ran a PCA and extracted the minimum number of components needed to secure the over-arching population level variation among the loci (`r pcadapt.params.LST[[MODE]]$min.variance.explained*10` % of the variation in loci). We then used Mahalanobis distances [@r398] to compute _P_ values and then q-values [using the \texttt{qvalue R} package; @r491]. Outlier loci were detected using a suitable FDR ($q < `r pcadapt.params.LST[[MODE]]$alpha.level`$).

After classifying loci as adaptive or neutral, we mapped the main gradients of the adaptive (if detected) and neutral genetic variation for each species. For each species, we discarded the population groupings, and partitioned adaptive and neutral loci into separate matrices. We used non-metric multi-dimensional scaling [NMDS; implemented in the \texttt{vegan R} package; @r458] using Gower distances [@r464; using the \texttt{cluster R} package to accommodate sparsity; @r457] to derive continuous variables that described the main gradients of adaptive and neutral genetic variation separately for each species (Table S2). To ensure that the ordinations described a sufficient amount of the genomic variation, we ran successive scaling analyses with increasing dimensionality until this was achieved (maximum stress value $\leq$ `r nmds.params.LST[[MODE]]$max.stress`; `r nmds.params.LST[[MODE]]$trymax` random starts for each analysis). Since each grid cell had up to three samples per species, we used the average of the ordinated values associated with the individuals in each grid cell to express the typical genomic characteristics of individuals in the cells.

@@

## Results
<!-- summary of methods -->
We successfully mapped the main spatial patterns of adaptive (if present) and neutral variation for each of the 26 species. The outlier detection methods detected adaptive genetic variation in `r as.character(as.english(length(env.surrogacy.LST)))` species. Generally, two outlier detection methods gave fairly consistent results (mean `r round(mean(spp.outlier.methods.congruence, na.rm=TRUE),2)` % loci per species $\pm$ `r round(sd(spp.outlier.methods.congruence, na.rm=TRUE),2)` SD). Of the species that were associated with adaptive genetic variation, only a few loci were detected as under selection (mean `r round(mean(spp.outlier.loci.props, na.rm=TRUE),2)` % loci per species $\pm$ `r round(sd(spp.outlier.loci.props, na.rm=TRUE),2)` SD). After identifying the loci under selection, we used NMDS analyses to identify the main gradients of adaptive (if detected) and neutral variation for each species. For all species in which we detected adaptive loci, only a couple of continuous dimensions were needed to sufficiently describe their patterns of adaptive genetic variation (Table S2). On the other hand, a few additional continuous dimensions were often needed to describe their patterns of neutral genetic variation (minimum $K = `r min(neutral.k)`$; mean $K = `r round(mean(neutral.k),2)`$; max $K = `r max(neutral.k)`$; Table S2). The ordinations resulting from the NMDS analyses were used to construct an adaptive (if present) and neutral genetic space for each species. The spatial distribution of these genetic spaces (Figures S29--S54) generally show patterns of spatial auto-correlation--especially the adaptive genetic spaces (eg.XXXX; SXX). Additionally, most species show east-west patterns in their intra-specific genetic variation (eg. XXXX; SXXX).

<!-- correlation analysis -->
The dissimilarity matrices generated using the environmental and geographic variables correlated with those matrices based on the genetic characteristics for most species (Table 1). Specifically, environmental variation was found to significantly correlate with adaptive genetic variation for `r as.character(as.english(sum(correlation.model.summary.DF$Environmental.corr.P<0.05,na.rm=TRUE)))` species (`r round((sum(correlation.model.summary.DF$Environmental.corr.P<0.05,na.rm=TRUE)/length(na.omit(correlation.model.summary.DF$Environmental.corr.P)))*100,2)` % associated with loci under selection; _P_ < 0.05; mean `r round(mean(filter(correlation.model.summary.DF, Environmental.corr.P<0.05)$Environmental.Marginal.R2),2)` marginal $R^2$ $\pm$ `r round(sd(filter(correlation.model.summary.DF, Environmental.corr.P<0.05)$Environmental.Marginal.R2),2)` SD for significant models). Additionally, geographic distances between planning units were found to significantly correlate with neutral genetic variation among planning units for `r sum(correlation.model.summary.DF$Geographic.corr.P<0.05,na.rm=TRUE)` species (`r round((sum(correlation.model.summary.DF$Geographic.corr.P<0.05)/length(na.omit(correlation.model.summary.DF$Geographic.corr.P)))*100,2)` % of all the species investigated; _P_ < 0.05; mean `r round(mean(filter(correlation.model.summary.DF, Geographic.corr.P<0.05)$Geographic.Marginal.R2),2)` marginal $R^2$ $\pm$ `r round(sd(filter(correlation.model.summary.DF, Geographic.corr.P<0.05)$Geographic.Marginal.R2),2)` SD for significant models). These results suggest that prioritizations with different environmental characteristics tend to have individuals with different adaptive genetic characteristics. Similarly, planning units that are further apart tend to have individuals with different neutral genetic characteristics. After verifying that the geographic and environmental variables generally correlated with genetic variation, our next step was to determine how effective these variables were as surrogates in the context of conservation planning.

<!-- surrogacy analysis -->
The environmental and geographic variables were moderately effective surrogates for genetic variation in most species (Figure 2). The relationship between the proportion of adaptive genetic variation secured in a prioritization and the proportion of environment variation it also secured was found to depend on the species for which the prioritization was generated (${\chi^2}_{`r env.surrogacy.AOV$df[[4]]`} = {`r round(env.surrogacy.AOV$Resid..Dev[[4]],2)`}; P `r pvalString(env.surrogacy.AOV$Pr..Chi.[[4]])`$). The slope for each species were all significantly different to zero (minimum \textit{z} = `r round(max(env.surrogate.spp.DF$statistic),2)`; maximum $P `r  pvalString(max(env.surrogate.spp.DF$p.value))`$; Table S3). The explanatory power of the environmental surrogates were also generally quite high for most species (mean `r round(mean(env.surrogate.spp.DF$r2CU),2)` $R^2$ $\pm$ `r round(sd(env.surrogate.spp.DF$r2CU),2)` SD; Figure S56). The nature of these relationships suggest that most of the adaptive variation for a given species can be secured in a prioritization using moderately high environmental-based targets ($geq 80$ %). Similarly, the proportion of neutral genetic variation in a prioritization was affected by the interaction between species and the proportion of neutral variation secured in the prioritization (${\chi^2}_{`r geo.surrogacy.AOV$df[[4]]`} = `r round(geo.surrogacy.AOV$Resid..Dev[[4]],2)`$; $P$ = `r pvalString(geo.surrogacy.AOV$Pr..Chi.[[4]])`). The slope for each species were also significantly different to zero (minimum \textit{z} = `r round(min(geo.surrogate.spp.DF$statistic),2)`$; maximum $P = `r pvalString(max(env.surrogate.spp.DF$p.value))`; Table S3). Generally, the explanatory power of geographic variables were higher than that of environmental variables (mean `r round(mean(geo.surrogate.spp.DF$r2CU),2)` $R^2 \pm$ `r round(sd(geo.surrogate.spp.DF$r2CU),2)` SD; Figure S57). Compared to the environmental variables, the slopes of the relationships suggest that very high geographic-based targets are required to generate prioritizations that secure a sufficient proportion of neutral genetic variation for most species ($geq 95$ %). Additionally, all species were associated with prioritizations that secured a large proportion of environmental or geographic variation (> 70 %), yet preserved only a very small proportion of the genetic variation (< 10 %; Figures SX and SX; such as _Gypsophila repens_ and _Luzula alpinopilosa_). These results suggest while prioritizations generated using surrogate-based targets tend to secure more genetic variation, prioritizations generated using just these targets can result in poor solutions.

### 2016-05-09 code/rmarkdown/figures.Rmd
+ article fixes + remove unneeded comments from MLPE.R
Former-commit-id: ee0043520642de57e7be9a2a46e563d35abc1e75

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=4.5, fig.cap='The relationship between surrogates and genetic variation secured in prioritizations. Panel (a) shows the relationship between the proportion of intra-specific adaptive genetic variation and environmental variation secured in a prioritization. Similarly, panel (b) shows the relationship between the proportion of intra-specific neutral variaiton and geograpgic variation secured in a prioritization. Panels (c) and (d) show the distribution of $R^2$ values for these models.'}
# make figure
p1 <- ggplot(aes(x=surrogate.held,y=genetic.held), data=env.surrogacy.DF) +
	xlab(expression(atop('Environmental variation','secured (%)'))) + 
	ylab('Adaptive genetic\nvariation secured (%)') +
	theme_classic() + theme(axis.line.x=element_line(color='black'),
		axis.line.y=element_line(color='black')) +
	geom_text(x=0.05, y=0.95, label='(a)') +
	coord_cartesian(xlim=c(0, 1))
for (i in seq_along(env.surrogacy.LST))
	p1 <- p1 + stat_smooth(method='glm', method.args=list(family='binomial'),
		data=filter(env.surrogacy.DF, Species==unique(Species)[i]),
		fullrange=TRUE, se=FALSE, colour='black')

p2 <- ggplot(aes(x=surrogate.held,y=genetic.held), data=geo.surrogacy.DF) +
	xlab(expression(atop('Geographic variation','secured (%)'))) + 
	ylab('Neutral genetic\nvariation secured (%)') +
	theme_classic() + theme(axis.line.x=element_line(color='black'),
		axis.line.y=element_line(color='black', colour='transparent')) +
	geom_text(x=0.05, y=0.95, label='(b)') +
	coord_cartesian(xlim=c(0, 1))
for (i in seq_along(geo.surrogacy.LST))
	p2 <- p2 + stat_smooth(method='glm', method.args=list(family='binomial'),
		data=filter(geo.surrogacy.DF, Species==unique(Species)[i]),
		fullrange=TRUE, se=FALSE, colour='black')

p1.hist <- ggplot(aes(r2CU),
		data=filter(env.surrogate.spp.DF, !is.na(r2CU))) +
	geom_histogram(fill='grey10', bins=5) +
	ylab('\nFrequency') + xlab(expression(atop('Effectiveness of environmental', variables~(R^2~coefficient)))) +
	theme_classic() + theme(axis.line.x=element_line(color='black'),
		axis.line.y=element_line(color='black'),
		plot.background=element_rect(fill='transparent', colour='transparent')) +
		geom_text(x=0.05, y=0.95, label='(c)') +
		coord_cartesian(xlim=c(0, 1))

p2.hist <- ggplot(aes(r2CU),
		data=filter(geo.surrogate.spp.DF, !is.na(r2CU))) +
	geom_histogram(fill='grey10', bins=10) +
	ylab('\nFrequency') + xlab(expression(atop('Effectiveness of geographic', variables~(R^2~coefficient)))) +
	theme_classic() + theme(axis.line.x=element_line(color='black'),
		axis.line.y=element_line(color='black'), 
		plot.background=element_rect(fill='transparent')) +
		geom_text(x=0.05, y=0.95, label='(d)') +
		coord_cartesian(xlim=c(0, 1))

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=4.5, fig.cap='The relationship between surrogates and genetic variation secured in prioritizations. Panel (a) shows the relationship between the proportion of intra-specific adaptive genetic variation and environmental variation secured in a prioritization. Similarly, panel (b) shows the relationship between the proportion of intra-specific neutral variaiton and geograpgic variation secured in a prioritization. Panels (c) and (d) show the distribution of $R^2$ values for these models.'}
# make figure
p1 <- ggplot(aes(x=surrogate.held,y=genetic.held), data=env.surrogacy.DF) +
	xlab('Environmental variation secured (%)') + 
	ylab('Adaptive genetic\nvariation secured (%)') +
	theme_classic() + theme(axis.line.x=element_line(color='black'),
		axis.line.y=element_line(color='black')) +
	geom_text(x=0.05, y=0.95, label='(a)') +
	coord_cartesian(xlim=c(0, 1))
for (i in seq_along(env.surrogacy.LST))
	p1 <- p1 + stat_smooth(method='glm', method.args=list(family='binomial'),
		data=filter(env.surrogacy.DF, Species==unique(Species)[i]),
		fullrange=TRUE, se=FALSE, colour='black')

p2 <- ggplot(aes(x=surrogate.held,y=genetic.held), data=geo.surrogacy.DF) +
	xlab('Geographic variation secured (%)') + 
	ylab('Neutral genetic\nvariation secured (%)') +
	theme_classic() + theme(axis.line.x=element_line(color='black'),
		axis.line.y=element_line(color='black', colour='transparent')) +
	geom_text(x=0.05, y=0.95, label='(b)') +
	coord_cartesian(xlim=c(0, 1))
for (i in seq_along(geo.surrogacy.LST))
	p2 <- p2 + stat_smooth(method='glm', method.args=list(family='binomial'),
		data=filter(geo.surrogacy.DF, Species==unique(Species)[i]),
		fullrange=TRUE, se=FALSE, colour='black')

p1.hist <- ggplot(aes(r2CU),
		data=filter(env.surrogate.spp.DF, !is.na(r2CU))) +
	geom_histogram(fill='grey10', bins=5) +
	ylab('\nFrequency') + xlab(expression(Environmental~variables~(R^2))) +
	theme_classic() + theme(axis.line.x=element_line(color='black'),
		axis.line.y=element_line(color='black'),
		plot.background=element_rect(fill='transparent', colour='transparent')) +
		geom_text(x=0.05, y=6, label='(c)') +
		coord_cartesian(xlim=c(0, 1))

p2.hist <- ggplot(aes(r2CU),
		data=filter(geo.surrogate.spp.DF, !is.na(r2CU))) +
	geom_histogram(fill='grey10', bins=10) +
	ylab('\nFrequency') + xlab(expression(Geographic~variables~(R^2))) +
	theme_classic() + theme(axis.line.x=element_line(color='black'),
		axis.line.y=element_line(color='black'), 
		plot.background=element_rect(fill='transparent')) +
		geom_text(x=0.05, y=8, label='(d)') +
		coord_cartesian(xlim=c(0, 1))

### 2016-05-09 code/rmarkdown/supporting_information.Rmd
+ article fixes + remove unneeded comments from MLPE.R
Former-commit-id: ee0043520642de57e7be9a2a46e563d35abc1e75

calc.fig.height <- function(i) {
	# init
	adapt.col <- paste0(unique(spp.samples.DF$species)[i], '_adaptive_d1')
	neutral.col <- paste0(unique(spp.samples.DF$species)[i], '_neutral_d1')
	n.plots <- 0 
	# count adaptive plot
	if (adapt.col %in% names(grid.FPLY))
		n.plots <- n.plots + spp.nmds.LST[[i]][['adaptive']]$ndim
	# count neutral plot
	if (neutral.col %in% names(grid.FPLY))
		n.plots <- n.plots + spp.nmds.LST[[i]][['neutral']]$ndim
	# exports
	return((((n.plots-1) %/% 4)+1) * 2)
}

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=2.5, fig.cap='The relationship between the proportion of adaptive genetic variation secured in a prioritizaiton and the proportion of environmental variation it also secures. Points represent values associated with randomly generated prioritizations. Blue lines indicate average trends computed using a generalised linear model with a logit link. Each panel shows data for a different species.'}
# format data
curr.DF <- env.surrogacy.DF %>% filter(!is.na(genetic.held)) %>% mutate(Species=gsub('_', ' ', Species))
curr.DF2 <- env.surrogate.spp.DF %>% filter(!is.na(r2CU)) %>% mutate(Species=gsub('_', ' ', Species))
curr.DF2$R2_repr <- round(curr.DF2$r2CU,2)
curr.DF2$R2_repr <- sapply(curr.DF2$R2_repr, function(x) {as.character(as.expression(substitute(~~italic(R)^2~"="~r2, list(r2=x))))})
curr.DF2$surrogate.held <- 0
curr.DF2$genetic.held <- 0.9

>>>>

calc.fig.height <- function(i) {
	# init
	adapt.col <- paste0(unique(spp.samples.DF$species)[i], '_adaptive_d1')
	neutral.col <- paste0(unique(spp.samples.DF$species)[i], '_neutral_d1')
	n.plots <- 0 
	# count adaptive plot
	if (adapt.col %in% names(grid.FPLY))
		n.plots <- n.plots + spp.nmds.LST[[i]][['adaptive']]$ndim
	# count neutral plot
	if (neutral.col %in% names(grid.FPLY))
		n.plots <- n.plots + spp.nmds.LST[[i]][['neutral']]$ndim
	# exports
	return((((n.plots-1) %/% 4)+1) * 2.5)
}

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=(2.5*4), fig.cap='The relationship between the proportion of adaptive genetic variation secured in a prioritizaiton and the proportion of environmental variation it also secures. Points represent values associated with randomly generated prioritizations. Blue lines indicate average trends computed using a generalised linear model with a logit link. Each panel shows data for a different species.'}
# format data
curr.DF <- env.surrogacy.DF %>% filter(!is.na(genetic.held)) %>% mutate(Species=gsub('_', ' ', Species))
curr.DF2 <- env.surrogate.spp.DF %>% filter(!is.na(r2CU)) %>% mutate(Species=gsub('_', ' ', Species))
curr.DF2$R2_repr <- round(curr.DF2$r2CU,2)
curr.DF2$R2_repr <- sapply(curr.DF2$R2_repr, function(x) {as.character(as.expression(substitute(~~italic(R)^2~"="~r2, list(r2=x))))})
curr.DF2$surrogate.held <- 0
curr.DF2$genetic.held <- 0.9
